A Switching Planner for Combined Task and Observation Planning

### 2010-11-19 code/subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/moritz_2011.tex
New bibliography, and reference to Andrew Ng. work with Mike Jordan...

@@

%%
Recently the system
\system{Conformant-FF}~\cite{hoffmann:brafman:2006}, demonstrated how
conformant planning ---i.e., serial planning in unobservable worlds---
can be modelled as a deterministic problem, and therefore solved using
serial systems. In this conformant setting, advances have been towards
compact representations and lazy evaluations of belief-states.

>>>>

Any (PO)MDP with stochastic actions can be compiled into an equivalent
deterministic-action POMDP with all the action uncertainty expressed
in the starting-state distribution~\cite{ng:Jordan:2000}. In our
setting, that of finite-horizon planning, this compilation yields a
finite flat representation of the POMDP. Therefore, although our
current implementation does not explicitly support it, our approach
generalises to POMDPs with stochastic action models.

@@

%%
Recently the systems
\system{Conformant-FF}~\cite{hoffmann:brafman:2006} and
$T_0$~\cite{palacios:geffner:2009}, demonstrated how conformant
planning ---i.e., serial planning in unobservable worlds--- can be
modelled as a deterministic problem, and therefore solved using serial
systems. In this conformant setting, advances have been towards
compact representations and lazy evaluations of beliefs.
